\documentclass{resume} % Use the custom resume.cls style
\usepackage{enumitem}
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}


\name{Albin P James} % Your name
\address{Thiruvananthapuram, Kerala, India \\ 9447029214 \\ albinpjames@outlook.com} % Your secondary addess (optional)
\address{https://github.com/albinpjames/ \\ https://linkedin.com/in/albinpjames/}  % Your phone number and email

\begin{document}

\begin{rSection}{Education}
{\bf Master's in Physics }, National Institute of Technology, Calicut (NITC) \hfill {10/2020 - 05/2022} \\
{\bf Bachelor’s in Physics}, St. Berchmans’ College, Kerala \hfill {06/2017 - 04/2020}\\
{\bf Senior Secondary}, Navajeevan Bethany Vidayalay CBSE, Nalanchira, Kerala \hfill {05/2017}
\end{rSection}

\begin{rSection}{ACADEMIC ACHIEVEMENTS}
\textbf{JEST} All India Rank \textbf{253} \hfill 2020 \\
\textbf{JAM} All India Rank \textbf{1116} \hfill 2020

\end{rSection}

\begin{rSection}{AREAS OF INTEREST }
Astrophysics and Cosmology \textbar{} Computational Physics  \textbar{} Scientific Computing \textbar{} History \& Philosohy of Science
\end{rSection}

\begin{rSection}{RESEARCH \& PROJECT EXPERIENCE}


\textbf {Statistical Properties of Dark Matter Halos from Cosmological Simulations}\hfill 07/2021 - 04/2022 \\ 
MSc Dissertation \\
Supervisor: Dr Charles Jose, Assistant Professor, CUSAT \\
In the theory of cosmological structure formation, galaxies form in gravitationally bound dark matter clumps called dark matter halos. In this project, we investigate the statistical properties of dark matter halos using numerical simulations. In particular, we estimate the halo mass function, which is the number density of dark matter halo within an infinitesimal logarithmic mass bin. The study uses the data from the AbacusSubmmit simulation. Using the Madhava high performance computing cluster, the data was analysed. Hence the halo mass functions for various redshifts of box sizes 500 MPc/h and 2000 MPc/h were computed. The statistical properties were further studied for redshifts 0.2 and 3 by dividing both the boxes into smaller boxes of 50, 25 and 20 MPc/h. \\


\textbf {Development of MATLAB code for the analysis of Magnetometer data}  \hfill 07/2019 - 05/2020 \\ 
BSc Dissertation\\
Supervisor: Dr Lijo Jose, Assistant Professor, SB College \\ 
The data was analysed using MATLAB Codes. Te output was manipulated and plotted using Origin Pro. Sensys FGM3D TD magnetometers of Space Physics Laboratory, VSSC Trivandrum placed at Changanassery SB College and Kannur were used to collect the data. The analysis of the magnetometer data during the solar eclipse using the code showed a drastic variation of the ionosphere compared to an average day. 
\end{rSection} 

\begin{rSection}{Professional Certification}

\textbf{Google IT Support Professional Certification} \hfill 07/2020\\
Google and offered through Coursera 
\begin{enumerate}
	\itemsep-0.25cm
	\item Technical Support Fundamentals
	\item Operating Systems and You: Becoming a Power User
	\item IT Security: Defense against the digital dark arts
	\item System Administration and IT Infrastructure Services
	\item The Bits and Bytes of Computer Networking
\end{enumerate}

\end{rSection}

\begin{rSection}{TECHNICAL SKILLS \& EXPERTISE}{}
	Programming Languages:\\ 
	Advanced: Python, C++  \textbar{}  Intermediate: MATLAB, LaTeX \textbar{} Basic: C, HTML, CSS  
	
	\item Miscellaneous: Origin Pro, Slrum \\
	Simulations \& Python Packages : GADGET 2, NgenIC, abacusnbody, astropy etc... \\
	Platforms: Linux, Windows, MS Office \\ 
	Visual \& Graphics: After Effects, Premier Pro, Photoshop, Illustrator 
\end{rSection}

\begin{rSection}{Certifications}
\textbf{Data-driven Astronomy }\hfill Ongoing\\
The University of Sydney through Coursera \\
\textbf{From the Big Bang to Dark Energy }\hfill 06/2020\\
The University of Tokyo through Coursera \\
\textbf{Understanding Research Methods }\hfill 04/2020\\
University of London and SOAS University of London offered through Coursera  \\
\textbf{Psychological First Aid} \hfill 12/2019\\
Johns Hopkins University and offered through Coursera \\
\textbf{Philosophy and the Sciences: Introduction to the Philosophy of Physical Sciences } \hfill 08/2019\\
The University of Edinburgh and offered through Coursera  \\
\textbf{Introduction to Psychology }\hfill 07/2019\\
Yale University and offered through Coursera 
\end{rSection}


\begin{rSection}{MEMBERSHIPS}
\textbf{Breakthrough Science Society, Trivandrum Chapter} \hfill 5/2021
\begin{itemize}[noitemsep,topsep=-0.2cm]
	\itemsep-0.05cm
	\item To promote science among students \& general public.
	\item To provide students access to seminars and talks by notable researchers free of cost.
\end{itemize}
\end{rSection}

\begin{rSection}{POSITIONS OF RESPONSIBILITIES}
	
	\textbf{Deputy Speaker } \hfill 2021-2022\\
	Student Affairs Council (SAC) - NIT Calicut,
	\begin{itemize}[noitemsep,topsep=-0.2cm]
		\itemsep-0.25cm
		\item I was entrusted with coordinating all the activities pertaining to student body including the research community. 
	\end{itemize}
	
	\textbf{Student Coordinator  } \hfill 2018-2020\\
	Science Centre- St Berchmans College, Changanassery,
	\begin{itemize}[noitemsep,topsep=-0.2cm]
		\itemsep-0.05cm
		\item I researched and hosted an Inter departmental science quiz. 
		\item Organised an Astronomy workshop and various sky watching sessions. 
		\item Hosted science exhibitions as part of the science centre. 
	\end{itemize}
	
	\textbf{Secretary} \hfill 2019-2020\\
	Physics Department Association- St Berchmans College, Changanasserry 
	\begin{itemize}[noitemsep,topsep=-0.2cm]
		\itemsep-0.05cm
		\item I was instrumental in initiating several programmes and activities in the college on behalf of the association. 
		\item Organized an All Kerala Inter Collegiate Quiz and presentation competition. 
	\end{itemize}

	
	\textbf{HRD Team Excellence Member } \hfill 2018-2019\\
	Human Resource Department- St Berchmans College, Changanasserry \\
	Every programmes in the college are carried out by a group of 20 students selected by the Human Resource Department of the college known as 'Team Excellence'. 
	\begin{itemize}[noitemsep,topsep=-0.2cm]
		\itemsep-0.05cm
		\item I was able to co-ordinate with my team to organize several programmes in the college. 
		\item Organized several National and International seminars in the college. 
	\end{itemize}
\end{rSection}

\begin{rSection}{ACHIEVEMENTS }
\textbf{MG University Kalolsavam Quiz}\\
Represented St Berchmans College at MG University Kalolsavam and bagged the runner up position for the consecutive years 2019 and 2020. \\
\textbf{Winner - Major Science  Quiz Competitions }\\
Won prizes for all major quiz competitions conducted across Kerala. Mainly the one focusing on science. Space and physics quiz are my forte.\\
\textbf{Best Outgoing Student}\\
The best outgoing student of Navajeevan Bethany Vidyalaya during the academic year 2016-2017.\\
\end{rSection} 


\begin{rSection}{CONFERENCES AND WORKSHOPS }
	\textbf{Sagan Exoplanet Summer Workshop on "Circumstellar Disks and Young Planets"} \hfill 2021\\
	NASA Exoplanet Science Institute, California Institute of Technology in Pasadena, CA.  \\
	\textbf{IIA Summer Programme 2021}\hfill 2021\\
	Indian Institute of Astrophysics  \\
	\textbf{E-Workshop on LaTeX 2021 }\hfill 2021\\
	GITAM Deemed to be University \\
	\textbf{Creative Science Workshop 2012 } \hfill 2012\\
	Kerala State Science and Technology Museum (KSSTM), Trivandrum \\
\end{rSection}


\begin{rSection}{Courses}
	Numerical \& Computational Physics \textbar{} Astrophyics \textbar{} General Relativity \textbar{} Classical Mechanics \textbar{} Electromagnetic Theory \textbar{} Mathematical Physics \textbar{} Nuclear and particle Physics \textbar{}
	Quantum Mechanics \textbar{} Condensed Matter Physics.
\end{rSection}


\end{document}
